---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# threshtools

<!-- badges: start -->
<!-- badges: end -->

This package was built to aid users in calculating and evaluating activity level thresholds for epidemiological surveillance data. It should be used alongside functions from the {mem} package and includes some useful functions for tidying up `memmodel` outputs.

## Installation

You can install the development version of threshtools from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("matthh10/threshtools")
```

## Example

This is a basic example which shows you how to check for overlapping thresholds:

```{r example-check_thresholds}
library(threshtools)

x <- dplyr::tibble(
  indicator = c("a", "b"),
  low = c(0.5, 1.2),
  medium = c(1.1, 0.8),
  high = c(2.5, 3.1),
  very_high = c(3.7, 4.2)
)

check_thresholds(x)
```

or covert count tables to format accepted by `mem:memmodel()`

```{r example-data_to_mem}
x <- tibble::tribble(
  ~week, ~year, ~flu_season,  ~rate,
  40,    2023,  "2023/2024",  2.5,
  41,    2023,  "2023/2024",  3.1,
  42,    2023,  "2023/2024",  4.2,
  40,    2024,  "2024/2025",  2.5,
  41,    2024,  "2024/2025",  3.1,
  42,    2024,  "2024/2025",  4.2,
  40,    2025,  "2025/2026",  2.5,
  41,    2025,  "2025/2026",  3.1,
  42,    2025,  "2025/2026",  4.2,
)


data_to_mem(
  x,
  seasons = c("2023/2024", "2024/2025"),
  week_col = week,
  year_col = year,
  season_col = flu_season,
  rate_col = rate,
  season_length = 33
)
```

or quickly find out the flu season that a date belongs to

```{r example_find_flu_season}

find_flu_season(as.Date("2023-11-15"), start_week = 40) # Expected: "2023/2024"


```

