---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# threshtools

<!-- badges: start -->
<!-- badges: end -->

This package was built to aid users in calculating and evaluating activity level thresholds for epidemiological surveillance data. It should be used alongside functions from the {mem} package and includes some useful functions for tidying up `memmodel` outputs.

## Installation

You can install the development version of threshtools from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("matthh10/threshtools")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(threshtools)

x <- dplyr::tibble(
  indicator = c("a", "b"),
  low = c(0.5, 1.2),
  medium = c(1.1, 0.8),
  high = c(2.5, 3.1),
  very_high = c(3.7, 4.2)
)

check_thresholds(x)


```

